### 2019-06-17 2-Chapters/1-Chapter/chapter1.tex
Illustrations

\paragraph{From Machine Learning to Reinforcement Learning.}
%
Similarly, we can narrow down the second field of study of this thesis, steps by steps.
Starting from the general concept of Machine Learning (ML), we focused our interest to statistical learning, then sequential learning, then Reinforcement Learning (RL, \cite{SuttonBarto2018}), then RL with limited feedback and finally to multi-armed bandits learning.
The reference book on RL is \cite{SuttonBarto2018}, so let us quote the definition of RL given by Richard Sutton and Andrew Barto:
\emph{``Reinforcement learning is learning what to do -— how to map situations to actions -— so
as to maximize a numerical reward signal. The learner is not told which actions to
take, but instead must discover which actions yield the most reward by trying them''}.
% - apprentissage statistique (machine learning) > séquentiel > par renforcement > information partielle (bandits)

@@

\tikzstyle{block} = [align=center, draw, fill=gray!25, rectangle, minimum height=3em, minimum width=6em]
\begin{figure}[h!]
    \centering
    \resizebox{0.30\textwidth}{!}{
        \begin{tikzpicture}[auto,node distance=5cm,>=latex,scale=1.5]
            %
            % We start by placing the blocks
            \node [block] (player) at (0,0) {Player};
            % We draw an edge between the player and system block to
            \node [block] (environment) at (2,0) {Environment};
            % Once the nodes are placed, connecting them is easy.
            \draw [->] (player) to[bend left=90] node[pos=0.5] {Action} (environment);
            \draw [->] (environment) to[bend left=90] node[pos=0.5] {Reward} (player);
            %
        \end{tikzpicture}
    }
\caption{Reinforcement learning cycle.}
\label{fig:1:ReinforcementLearningCycle}
\end{figure}

>>>>

\paragraph{From Machine Learning to Reinforcement Learning.}
%
Similarly, we can narrow down the second field of study of this thesis, steps by steps.
Starting from the general concept of Machine Learning (ML), we focused our interest to statistical learning, then sequential learning, then Reinforcement Learning (RL, \cite{SuttonBarto2018}), then RL with limited feedback and finally to multi-armed bandits learning.
As illustrated in Figure~\ref{fig:1:MainTypesOfMachineLearning}, there are other types of ML, that we do not focus on in this thesis.
The reference book on RL is \cite{SuttonBarto2018}, so let us quote the definition of RL given by Richard Sutton and Andrew Barto:
\emph{``Reinforcement learning is learning what to do -— how to map situations to actions -— so
as to maximize a numerical reward signal. The learner is not told which actions to
take, but instead must discover which actions yield the most reward by trying them''}.
% - apprentissage statistique (machine learning) > séquentiel > par renforcement > information partielle (bandits)

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.45\textwidth]{Illustration_of_Machine_Learning_and_Reinforcement_Learning.jpg}
\caption{Main types of Machine Learning, \copyright{} from \href{https://vas3k.com/blog/machine_learning/}{\texttt{VAS3k.com/blog/machine\_learning}}.}
\label{fig:1:MainTypesOfMachineLearning}
\end{figure}

% Modified from the https://draw.io/ map from
% https://github.com/trekhleb/homemade-machine-learning/blob/master/images/machine-learning-map.xml
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.90\textwidth]{machine-learning-map.pdf}
\caption{Classification of the main types of Machine Learning: MAB is a subset of Reinforcement Learning and RL is a subset of ML.}
\label{fig:1:MainTypesOfMachineLearning2}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.20\textwidth]{Illustration_of_Reinforcement_Learning_action-reward_loop.png}
    \caption{Reinforcement learning cycle, a learner interacts with its environment through actions, and observes a reward, iteratively. \copyright{} from \href{https://vas3k.com/blog/machine_learning/}{\texttt{VAS3k.com/blog/machine\_learning}}.}
    \label{fig:1:ReinforcementLearningCycle}
\end{figure}

% \tikzstyle{block} = [align=center, draw, fill=gray!25, rectangle, minimum height=3em, minimum width=6em]
% \begin{figure}[h!]
%     \centering
%     \resizebox{0.30\textwidth}{!}{
%         \begin{tikzpicture}[auto,node distance=5cm,>=latex,scale=1.5]
%             %
%             % We start by placing the blocks
%             \node [block] (player) at (0,0) {Player};
%             % We draw an edge between the player and system block to
%             \node [block] (environment) at (2,0) {Environment};
%             % Once the nodes are placed, connecting them is easy.
%             \draw [->] (player) to[bend left=90] node[pos=0.5] {Action} (environment);
%             \draw [->] (environment) to[bend left=90] node[pos=0.5] {Reward} (player);
%             %
%         \end{tikzpicture}
%     }
% \caption{Reinforcement learning cycle.}
% \label{fig:1:ReinforcementLearningCycle}
% \end{figure}

### 2019-06-17 2-Chapters/2-Chapter/chapter2.tex
Illustrations

% - Worst case regret (max $R_T^{r}$ for $r$ index of Monte-Carlo simulation?)
The \textbf{switching cost} $\mathrm{SC}^{\cA}(T)$ counts how many times the player's decision has changed from one round to the next one, \ie, $\mathrm{SC}^{\cA}(T) \eqdef \sum_{t=1}^{T-1} \indic(A(t) \neq A(t+1))$.
It has recently gained interest in the literature, for instance the authors of \cite{Koren17} proposed an algorithm that adaptively tries to balance the trade-off between minimizing the regret and minimizing the switching cost.
%
Indeed, in single-player models it is easy to show that achieving logarithmic regret directly implies a logarithmic upper-bound on the switching cost, and conversely the lower-bound from \cite{LaiRobbins85} also gives an asymptotic logarithmic lower-bound.
But even if $\mathrm{SC}^{\cA}(T) = \Theta(\log T)$ for an efficient algorithm, it can be interesting to numerically evaluate this quantity, as a large value might indicate an algorithm that is alternating too much between the optimal arm and other arms.
%
% \TODOL{Enlever ça, juste une phrase qui dit "on le fait plus tard".}
We find more interesting to study $\mathrm{SC}^{\cA_1,\dots,\cA_M}(T)$, the sum of the switching costs of the $M$ players in a multi-players bandit game (if player $j$ uses algorithm $\cA_j$ for $j=1,\dots,M$), as studied in Chapter~\ref{chapter:5}.
% Indeed in this case it is possible that the players attain a logarithmic centralized regret, by following an efficient centralized or decentralized algorithm, while still suffering from a linear switching cost.
% %
% It is very satisfying to obtain a logarithmic switching cost for our algorithm \MCTopM-\klUCB{} in Chapter~\ref{chapter:5}, even if minimizing the switching cost was not one of our objective, and the bound we obtain on $\mathrm{SC}^{\cA_1,\dots,\cA_M}(T)$ is just a consequence of our proof of the control we give on the regret $R^{\cA}(T)$.
% % - Switching cost? \cite{modiDemo2016} \cite{Koren17}
% On a more experimental note, it was shown in \cite{modiDemo2016} that the previous state-of-the-art policy for multi-players bandits, \rhoRand, could be tuned to run in batches\footnote{~The batch bandit setting implies that all players use the same decisions for instance for $50$ consecutive times, and update their decisions only once every $50$ time steps. For more details, see \cite{modiDemo2016} for experiments on the multi-players case, or \cite{perchet2016,gao2019batched,kolnogorov2019multi} for theoretical developments on the single-player case.}, in order to reduce by a certain multiplicative factor its switching cost while only adding an additive factor on its regret. While such ideas can interest a practitioner, they does not change the asymptotic behavior of $\mathrm{SC}^{\cA_1,\dots,\cA_M}(T)$, which is $\Theta(\log(T))$ for any efficient policy.

@@

This Section starts by discussing two naive strategies which fail dramatically,
%
and then we present two simple strategies which performs efficiently, only if they are tuned using a prior knowledge of the problem difficulty, but are thus unusable for practical applications.
%
We focus then on index policies, with a first efficient policy, $\UCB_1$, that uses upper confidence bounds (UCB) on the means estimates, and is known to be order-optimal for bounded rewards.
Two other well-known and optimal algorithms are exposed: \klUCB{} extends the idea of $\UCB_1$ but use tighter confidence intervals and thus it typically obtains better theoretical results, and Thompson sampling which replaces the principle of ``optimism under uncertainty'' by a Bayesian point-of-view.
%
Finally, we conclude by briefly exposing other families of algorithms.

>>>>

% - Worst case regret (max $R_T^{r}$ for $r$ index of Monte-Carlo simulation?)
The \textbf{switching cost} $\mathrm{SC}^{\cA}(T)$ counts how many times the player's decision has changed from one round to the next one, \ie, $\mathrm{SC}^{\cA}(T) \eqdef \sum_{t=1}^{T-1} \indic(A(t) \neq A(t+1))$.
It has recently gained interest in the literature, for instance the authors of \cite{Koren17} proposed an algorithm that adaptively tries to balance the trade-off between minimizing the regret and minimizing the switching cost.
%
Indeed, in single-player models it is easy to show that achieving logarithmic regret directly implies a logarithmic upper-bound on the switching cost, and conversely the lower-bound from \cite{LaiRobbins85} also gives an asymptotic logarithmic lower-bound.
But even if $\mathrm{SC}^{\cA}(T) = \Theta(\log T)$ for an efficient algorithm, it can be interesting to numerically evaluate this quantity, as a large value might indicate an algorithm that is alternating too much between the optimal arm and other arms.
%
% \TODOL{Enlever ça, juste une phrase qui dit "on le fait plus tard".}
Because it is relevant for cognitive radio applications, as a hardware reconfiguration costs energy, and so changing channel from two consecutive time steps has a non trivial energy cost, as highlighted in \cite{modiDemo2016}.
And thus we find more interesting to study $\mathrm{SC}^{\cA_1,\dots,\cA_M}(T)$, the sum of the switching costs of the $M$ players in a multi-players bandit game (if player $j$ uses algorithm $\cA_j$ for $j=1,\dots,M$), as studied in Chapter~\ref{chapter:5}.
Our proposed algorithm, \MCTopM, achieves order-optimal logarithmic regret as well as a logarithmic number of switches.
% Indeed in this case it is possible that the players attain a logarithmic centralized regret, by following an efficient centralized or decentralized algorithm, while still suffering from a linear switching cost.
% %
% It is very satisfying to obtain a logarithmic switching cost for our algorithm \MCTopM-\klUCB{} in Chapter~\ref{chapter:5}, even if minimizing the switching cost was not one of our objective, and the bound we obtain on $\mathrm{SC}^{\cA_1,\dots,\cA_M}(T)$ is just a consequence of our proof of the control we give on the regret $R^{\cA}(T)$.
% % - Switching cost? \cite{modiDemo2016} \cite{Koren17}
% On a more experimental note, it was shown in \cite{modiDemo2016} that the previous state-of-the-art policy for multi-players bandits, \rhoRand, could be tuned to run in batches\footnote{~The batch bandit setting implies that all players use the same decisions for instance for $50$ consecutive times, and update their decisions only once every $50$ time steps. For more details, see \cite{modiDemo2016} for experiments on the multi-players case, or \cite{perchet2016,gao2019batched,kolnogorov2019multi} for theoretical developments on the single-player case.}, in order to reduce by a certain multiplicative factor its switching cost while only adding an additive factor on its regret. While such ideas can interest a practitioner, they does not change the asymptotic behavior of $\mathrm{SC}^{\cA_1,\dots,\cA_M}(T)$, which is $\Theta(\log(T))$ for any efficient policy.

@@

This Section reviews the most important families of stochastic MAB algorithms, from naive and simple strategies, to strategies based on the optimism or the Bayesian principles, to recent ``best-of-both-worlds'' strategies.
% starts by discussing two naive strategies which fail dramatically,
% %
% and then we present two simple strategies which performs efficiently, only if they are tuned using a prior knowledge of the problem difficulty, but are thus unusable for practical applications.
% %
% We focus then on index policies, with a first efficient policy, $\UCB_1$, that uses upper confidence bounds (UCB) on the means estimates, and is known to be order-optimal for bounded rewards.
% Two other well-known and optimal algorithms are exposed: \klUCB{} extends the idea of $\UCB_1$ but use tighter confidence intervals and thus it typically obtains better theoretical results, and Thompson sampling which replaces the principle of ``optimism under uncertainty'' by a Bayesian point-of-view.
% %
% Finally, we conclude by briefly exposing other families of algorithms.
